Adopting agile in the large: motivations, success factors and challenges

### 2014-05-12 journal/article.tex
Requirements engineering challenges: Completed

Maples [P31] describes that marketing needed three months for preparing the
product launch, but the agile process allowed development to keep changing the
content of the product. As a result marketing was struggling with creating
material and campaigns without knowing the exact product features. Further, the
processes of acquiring export clearances and licensing authority required that
the the feature set of the product was known well on beforehand [P31].
As a result of these requests development felt that their process was being
slowed down. The issues were solved by agreeing on that marketing could at any
time request a release in 90 days, and development would be able to commit to a
fixed feature set to be delivered [P31].

@@

@@

"C: Adapting non-development parts of organization to agile"

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MARKETING NEEDS TO KNOW ON BEFOREHAND WHAT WILL BE RELEASED
% 
% 
% * Problem: Teams completed backlog --> Continued with stories direct from customer --> Single customer bias
% * Problem: Sales and marketing organization had a different vision of the product
% * Problem: Product marketing was not collaborative, and in old mindset
% * Problem: Requirements --> user stories more granular and prioritized
% [P31]
% After several months of working on the new products, the Agile teams “drained”
% the backlog.   For a while, they kept busy working on new user stories that came
% directly from the strategic customer.  This began to lead to a disconnect
% between what the marketing and sales organizations believed to be the overall
% direction of the product, and the actual direction it was taking based on the
% needs of a single customer. It was clearly time for a regroup, and the
% engineering team pushed back on the MRD.  They were in full production mode
% using Agile and they needed more granular, prioritized user stories to fuel
% their efforts.  The teams needed product marketing to be more collaborative in
% the decomposition of the requirements. This was a totally foreign concept for
% the product marketing team. They had approached the relationship with
% engineering as a “black box” – high level requirements went in, and something
% eventually came out (usually late, and sometimes off the mark on what they
% expected).
% 
% 
% * Challenge: Accomodate time for export clearance
% * Challenge: Acquire third-party licensing authority --> prior to product release
% * Challenge: These processes will remain traditional
% * Challenge: Marketing needs some lead time
% * Enablement activities (sales materials, training)
% * These steps take time, but they are part of the product lifecycle
% * Challenge: Must know beforehand what will be in the product
% [P31]
% While changing our process in the front end of the value chain began to yield
% success, we discovered that there was also a traditional wall at the back end:
% our product release process.
% While the Agile approach enables teams to be flexible with regard to
% prioritization, and very adaptive to changing market conditions and customer
% needs, there are certain “laws of physics” required to release commercial
% product that cannot be altered. For example, the time required to acquire export
% clearance or to acquire third-party licensing authority prior to product
% release.  As a vendor that makes products that must be marketed, sold and
% implemented, there are several traditional processes that are involved in
% releasing our products to market.
% 
% First there are the regulatory requirements such as export compliance relative
% to exporting code with certain levels of encryption,  then there are the
% marketing launch plans (demand generation campaigns, collateral, Web site,
% public relations), and finally, the field enablement activities (sales
% materials, training).  All these initiatives take time, and they cannot begin
% without knowledge of exactly what is going to be in the product.
% 
% 
% * Problem: Marketing had to know on beforehand what will be in the release
% * Problem: Business went with requiring a fixed delivery date and a fixed feature set
% [P31]
% Serious friction arose. The development teams became frustrated because they
% felt marketing and the NPI process was stalling their progress and throwing up
% barriers against the core principles they had adopted.  Marketing, who needed to
% begin prepping for the launch of the product about three months before the
% actual date, found themselves struggling to message and develop materials and
% campaigns without a clear understanding of the features and functionality that
% would actually be “ready” on the release date. And, the NPI group could not
% apply for export compliance nor could they request any third party license
% authorization without knowing what was actually going to be in the product.
% 
% 
% * Solution: Development and product marketing work together
% * Solution: Product marketing can require a release to be completed in 90 days
% [P31]
% What we instituted was what we call an “Iron Triangle.” The concept is that at
% some number of sprints out before a release, we would commit to delivering a
% fixed set of features and functionality  at a certain date.  Of course, there
% was always the opportunity for us to deliver more than what we committed to, 
% but we absolutely had to deliver the set features by the set date.
% 
% If  product marketing wants to release product for any reason they can “declare”
% a release date, and  we’re able to lock the current feature set and have  the
% code ready to release within two sprints of the date they declare the release
% necessary.

@@

REQUIREMENT AND MRD COMMUNICATION PROBLEMS

* Not agile: MRDs --> Stories had to be extracted from detailed documentation --> Not good
* MRDs not based on reality
[P2]
Extracting user stories from existing, very detailed ‘marketing requirements
documents’ (MRDs) was another workaround. These MRDs were a prominent artifact
found across the organisation. Leaders of Project Z claimed that it was very
difficult to work with such detailed documents in a project whose scope could
change rapidly; one agile developer described MRDs as “not based in reality at
all”.
Comment:
The problem with MRDs is a symptom of the challenge to integrate "the business" with the agile process.

* Problem: MRD is not dynamic
* Problem: MRD requirements scoped once a year --> Teams decide for themselves
* Problem: Product marketing team was very disrupted of the requirement of collaboration!
[P31]
Further, the MRD needed to be more dynamic. Because the teams had achieved a
predictable, efficient pace of delivery, scoping the requirements of a release
once a year wasn’t enough to feed the engine.  Without the proper fuel the teams
were left to decide for themselves what new things to work on, driving further
disconnect between the groups. The concept of continuous collaboration
throughout the development cycle was a very disruptive concept for the product
marketing team.

* Problem: Teams completed backlog --> Continued with stories direct from customer --> Single customer bias
* Problem: Sales and marketing organization had a different vision of the product
* Problem: Product marketing was not collaborative, and in old mindset
* Problem: Requirements --> user stories more granular and prioritized
[P31]

* Requirements engineering must be done differently
[P45]
Product teams had to communicate with business management, marketing, and field
services who were not fully prepared for how Scrum and the product teams’
expectations would change their daily work. The process of software requirements
engineering were found to require a major adjustment.

>>>>

Maples [P31] describes that marketing needed three months for preparing the
product launch, but the agile process allowed development to keep changing the
content of the product. As a result marketing was struggling with creating
material and campaigns without knowing the exact product features. Further, the
processes of acquiring export clearances and licensing authority required that
the the feature set of the product was known well on beforehand.
As a result of these requests development felt that their process was being
slowed down. The issues were solved by agreeing on that marketing could at any
time request a release in 90 days, and development would be able to commit to a
fixed feature set to be delivered [P31].

% Requirements engineering is difficult

In agile methods requirements engineering is usually closely tied to the
development team. However, large development projects will demand additional
high level requirements management.
This is apparent in cases where complexity of the product will require
additional layers of product management [P45], requirements are created by
several stakehoder groups and development teams can not be in contact with all
of them [P39], or teams do not have access to stakeholders due to a distributed
seetting [P24].
As an integral part of the software development lifecycle, requirements
management will be affected by the new agile process. In large organizations
product and requirements management was initially done in a traditional way, but
it was contrasted by the agile process that required iteratively supplying small
requirements to development [P51]. The agile method had to be extended to
include a process on how to get large requirements into team backlogs [P31].

Requirements were in some cases first defined on a high level in marketing
requirements documents (MRD) [P1, P31] or functional specifications [P33]. These
high level requirements needed to be elaborated to be used by agile development
teams. The requirements breakdown in it self was found to be difficult [P1,
P33], and also when to do the breakdown and to which detail level [P17].
Product managers and business analysts were struggling in creating high level
requirements [P33, P37], and teams were struggling in breaking them down to an
estimable size [P33]. Smits and Rilliet [P48] describe how high level product
management delivered requirements in too large chunks resulting in development
teams spending large amounts of time on defining suitaby sized stories. In one
case the teams were overwhelmed by reprioritization and requirements bartering
when stakeholders learned that requirements could be rearranged flexibly [P31].

Several cases highlighted that much learning was needed to master the new
process of creating user stories, both on product management and development
levels [P27, P30, P33, P37]. There were problems such as ambiguity in
requirements [P5, P11], and effort estimation for stories was hard to do well
[P27, P37].

@@

Some cases reported  Some organizations used a quality assurance group separate
from development.

@@

@@
